\section{基本情况}
韩瑞冬，男，陕西西安人，1995年10月出生，西安电子科技大学网络与信息安全学院网络空间安全专业2020级博士研究生。
\section{教育背景}
2014.09～2018.07， 西北农林科技大学，本科，专业：计算机科学与技术
\par
2018.09～2020.07， 西安电子科技大学，硕士研究生，专业：计算机科学与技术
\par
2020.09～，西安电子科技大学，博士研究生，专业：网络空间安全
\section{攻读博士学位期间的研究成果}

\begin{enumerate}[label={[}\arabic*{]}]
    \item \underline{\textbf{Ruidong Han}}, Siqi Ma, Juanru Li, Surya Nepal, David Lo, Zhuo Ma, JianFeng Ma. 
    Range Specification Bug Detection in Flight Control System Through Fuzzing[J]. 
    IEEE Transactions on Software Engineering (TSE). 
    \textbf{CCF-A}. 

    \item \underline{\textbf{Ruidong Han}}, Chao Yang, Siqi Ma, JiangFeng Ma, Cong Sun, Juanru Li, Elisa Bertino. 
    Control Parameters Considered Harmful: Detecting Range Specification bugs in Drone[C]. 
    44th International Conference on Software Engineering (ICSE). 
    \textbf{CCF-A}.

    \item \underline{\textbf{Ruidong Han}}, Huihui Gong, Siqi Ma, Juanru Li, Chang Xu, Elisa Bertino, Surya Nepal, Zhuo Ma, Jianfeng Ma.
    A Credential Usage Study: Flow‑Aware Misuse Detection in Open‑Source Projects[J].
    IEEE Transactions on Information Forensics \& Security (TIFS).
    \textbf{CCF-A}.

    \item Di Lu, \underline{\textbf{Ruidong Han}}, Yulong Shen, Xuewen Dong, Jianfeng Ma, Xiaojiang          Du, Mohsen Guizani.
    xTSeH: A trusted platform module sharing scheme towards smart IoT‑eHealth devices[J].
    IEEE Journal on Selected Areas in Communications (JSAC).
    \textbf{CCF-A}.

    \item Di Lu, \underline{\textbf{Ruidong Han}}, Yue Wang, Yongzhi Wang, Xuewen Dong, Xindi Ma, Teng Li, Jianfeng Ma.
    A secured TPM integration scheme towards smart embedded system based collaboration network[J].
    Computers \& Security (C\&P).
    \textbf{CCF-B}.

    \item Taifeng Liu, Chao Yang, Xinjing Liu, \underline{\textbf{Ruidong Han}}, Jianfeng Ma.
    RPAU: Fooling the Eyes of UAVs via Physical Adversarial Patches[J].
    IEEE Transactions on Intelligent Transportation System (TITS).
    \textbf{CCF-B}.

    \item \underline{\textbf{Ruidong Han}}, Chao Yang, Jianfeng Ma, Siqi Ma, Yunbo Wang, Feng Li.
    IMShell-Dec: Pay More Attention to External Links in PowerShell[C].
    35th IFIP International Conference on ICT Systems Security and Privacy Protection (IFIP SEC).
    \textbf{CCF-C}.
    

\end{enumerate}

\section{参与科研项目}

[1] 无人系统高可信感知服务关键技术，国家自然基金重点项目（Key Program 62232013），进行中，学生参与人.

[2] 某研究项目, 某安全防护技术, 2019 年4 月至2020 年12 月, 结题, 学生参与
人.

